%-------------------------
% Resume in Latex - Tailored for Homeland Defender (Immigration Services Officer)
% Author : Trampas Kirk
% Adapted from: Amlaan Bhoi
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex, hidelinks]{hyperref}
\usepackage{fancyhdr}

\usepackage[charter]{mathdesign} % Bitstream Charter

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Fix footskip warning
\setlength{\footskip}{12pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.50in}
\addtolength{\evensidemargin}{-0.50in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemNoBullet}[2]{
  \item[]\small{
    \hspace{-9pt}\textbf{#1}{: #2 \vspace{-6pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item[]
  \begin{tabular*}{0.98\textwidth}{l@{\extracolsep{\fill}}r}
      \hspace{-10pt}\textbf{#1} & #2 \\
      \hspace{-10pt}\textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% custom commands
\newcommand{\shorterSection}[1]{\vspace{-10pt}\section{#1}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{center}
  \small \textbf{{\huge Trampas Kirk}} \\
    \vspace{2mm}
    \href{mailto:trampas.kirk@protonmail.com}{\color{blue}\underline{trampas.kirk@protonmail.com}} $\vert$
  LinkedIn: \href{https://www.linkedin.com/in/trampaskirk/}{\color{blue}\underline{trampaskirk}} $\vert$
  Github: \href{https://github.com/cynoclast}{\color{blue}\underline{https://github.com/cynoclast}} \\
    \vspace{1mm}
\end{center}

%-----------SKILLS-----------------
\shorterSection{Skills/Tools}
  \resumeSubHeadingListStart
  \small
    \item{
     \textbf{Languages/protocols}{: Java, bash, regular expressions, \LaTeX, PL/SQL, XML/XSLT}
     \hfill
    }
    \vspace{-5pt}
    \item{\textbf{Tools}{: UNIX/POSIX tools, git, postgres, Oracle, Jenkins/CI/CD, IntelliJ, Maven, research \& documentation tools, data analysis}}
    \vspace{-5pt}
    \item{
     \textbf{Operating Systems}{: Linux, Unix, Windows}
    }
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\shorterSection{Experience}

  \resumeSubHeadingListStart

    % Tailored summary for the role
    \resumeSubheading
        {Relevant Qualifications for Homeland Defender (Immigration Services Officer)}{}
        {Application Review, Adjudication \& Security Support}{}
        \resumeItemListStart
          \resumeItem{Application Adjudication \& Compliance}
              {Conducted thorough reviews of complex documentation, data, and records to ensure regulatory compliance. Skilled at verifying supporting materials, identifying inconsistencies, and determining eligibility against defined criteria.}
          \resumeItem{Security Vetting \& Research}
              {Supported U.S. Navy Aegis Weapon System projects (including classified work). Performed data extraction, complex queries, background-oriented analysis, and usage tracking to maintain system integrity and compliance.}
          \resumeItem{Decision Writing \& Analysis}
              {Produced clear, logical reports and documentation. Interpreted regulations, operating instructions, and technical requirements to support high-stakes decisions and stakeholder communications.}
          \resumeItem{Fraud Detection \& Process Integrity}
              {Built validation frameworks, reconciliation tools, and quality controls for financial/technical systems to detect anomalies and ensure data accuracy in regulated environments.}
          \resumeItem{Communication \& Collaboration}
              {Mentored teams, coordinated with stakeholders, and provided direct support across departments. Strong oral/written skills for interviews, reporting, and cross-functional problem solving.}
        \resumeItemListEnd

    \resumeSubheading
        {SquareTrade Inc.}{remote}
        {Lead Engineer}{Sept 2022 - Dec 2024}
        \resumeItemListStart
        \resumeItem{Engineering Leadership}
            {Led design and delivery of automation projects involving business logic, cross-team coordination, legacy system research, new service development, monitoring, and analytics improvements.}
        \resumeItemListEnd

    \resumeSubheading
      {Storygize, Inc.}{remote}
      {Senior Software Engineer}{Jun 2021 - Sept 2022}
      \resumeItemListStart
        \resumeItem{Engineering}
          {Developed enhancements for high-volume real-time platform including reporting, caching, integrations, and process automation. Improved reliability through testing and failure handling.}
      \resumeItemListEnd

    \resumeSubheading
      {Mainz Brady Group / Nike. Inc}{Beaverton, OR}
      {Senior Application Engineer}{Nov 2013 - May 2019}
      \resumeItemListStart
        \resumeItem{Microservices \& Legacy Systems}
          {Enhanced notification and product data services for international high-volume use. Introduced testing standards, architecture improvements, and domain modeling for better maintainability.}
      \resumeItemListEnd

    \resumeSubheading
      {Citigroup, Global Derivatives Market}{Charleston, SC}
      {Senior Programmer/Analyst}{Dec 2009 - Apr 2013}
      \resumeItemListStart
        \resumeItem{Compliance \& Reconciliation}
          {Developed reconciliation tools for FINRA regulatory reporting and automated data matching between systems. Created validation frameworks and testing tools widely adopted by the organization.}
      \resumeItemListEnd

    \resumeSubheading
      {BenefitFocus.com}{Charleston, SC}
      {Team Lead / Senior Software Engineer}{Oct 2005 - Dec 2009}
      \resumeItemListStart
        \resumeItem{EDI \& Data Processing}
          {Led team processing high-volume benefits data. Designed complex translation systems (Java, Oracle, XML/XSLT). Improved code quality, builds, and stakeholder coordination.}
      \resumeItemListEnd

    \resumeSubheading
      {MSIS Inc.}{Dahlgren, VA}
      {Software Engineer}{Fall 2004 - Fall 2005}
      \resumeItemListStart
        \resumeItem{U.S. Navy Aegis Support}
          {Contributed to classified projects with data extraction, complex queries, license optimization algorithms, and system performance enhancements across Unix/OpenVMS environments.}
      \resumeItemListEnd

    \resumeSubheading
      {King Brothers Fabricating Inc.}{Parkersburg, WV}
      {Structural Detailer}{Summer 1999 - Fall 2000}
      \resumeItemListStart
        \resumeItem{CAD Drafting}
          {Produced detailed structural drawings ensuring compliance with architectural and fabrication specifications.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd % Closing the Experience section

%-----------EDUCATION-----------------
\shorterSection{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {West Virginia Wesleyan College}{Buckhannon, WV}
      {Bachelor of Science, Computer Science}{Summer 2000 - Spring 2004}
  \resumeSubHeadingListEnd

%-----------PROJECTS AND HOBBIES-----------------
\shorterSection{Projects and Hobbies}
  \resumeSubHeadingListStart
  \small
    \item{Archery and Trap Shooting}
    \item{UNIX tools, dotfiles, and personal automation scripting}
    \item{Reading and Writing}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}